Supplementary material for Photographic Text-to-Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-11-15 supp.tex

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{2871} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{1}
\begin{document}
%\tableofcontents
%\blinddocument

%%%%%%%%% TITLE
%\title{Supplementary Materials for "Understanding, Describing, and Visualizing Medical Images Through Reading Diagnostic Report Text"}

%\author{First Author\\
%Institution1\\
%Institution1 address\\
%{\tt\small firstauthor@i1.org}
%% For a paper whose authors are all at the same institution,
%% omit the following lines up until the closing ``}''.
%% Additional authors and addresses can be added with ``\and'',
%% just like the second author.
%% To save space, use either the email address or home page, not both
%\and
%Second Author\\
%Institution2\\
%First line of institution2 address\\
%{\tt\small secondauthor@i2.org}
%}

%\maketitle
%\thispagestyle{empty}

@@

%%%%%%%%% BODY TEXT
\begin{appendices}

@@

%\renewcommand{\thechapter}{A\arabic{chapter}}
\section{Results on the CUB bird dataset}

\end{appendices}

>>>>

%\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{2823} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi

\setcounter{page}{1}
\begin{document}
%\tableofcontents
%\blinddocument

%%%%%%%%% TITLE
%\title{Supplementary Materials for "Understanding, Describing, and Visualizing Medical Images Through Reading Diagnostic Report Text"}
\title{Supplementary material for Photographic Text-to-Image Synthesis \\ with a Hierarchically-nested Adversarial Network}
%\author{First Author\\
%Institution1\\
%Institution1 address\\
%{\tt\small firstauthor@i1.org}
%% For a paper whose authors are all at the same institution,
%% omit the following lines up until the closing ``}''.
%% Additional authors and addresses can be added with ``\and'',
%% just like the second author.
%% To save space, use either the email address or home page, not both
%\and
%Second Author\\
%Institution2\\
%First line of institution2 address\\
%{\tt\small secondauthor@i2.org}
%}

\maketitle
%\thispagestyle{empty}

@@

%%%%%%%%% BODY TEXT

@@

%\renewcommand{\thechapter}{A\arabic{chapter}}
\section{Results on the CUB Bird Dataset}

\section{Results on the Oxford-102 Flower Dataset}
